Argennon: A Scalable Smart Contract Platform

### 2022-04-01 tex/sections/avm.tex
Add introduction for three-step request execution
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

\section{Parallel Request Execution}\label{sec:concurrency}
\input{sections/concurrency}

>>>>

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data structures for executing requests are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure. In the final step, request are executed using this data structure and helper data structures built in the
first step.

@@

\section{Data Dependency Analysis}\label{sec:concurrency}
\input{sections/concurrency}
